Composable Concurrency Models

### 2016-11-18 slides/slides.tex
Added slide about threading and prepped some other stuff for the last practice talk

\usepackage{appendixnumberbeamer}
\usepackage[USenglish]{babel}
\usepackage[backend=bibtex,citestyle=authortitle]{biblatex}
\usepackage[scale=2]{ccicons}
\usepackage{color}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{multicol}
\usepackage{pifont}
\usepackage{tikz}
\usetikzlibrary{positioning}

@@

@@

  \begin{frame}
    \frametitle{Composability criteria}
    \centering
    \small

@@

    \textbf{Pairwise combinations of four Clojure concurrency models:}
    \vfill
    \begin{tabular}{c | c c c c | c c c c}
      & \multicolumn{4}{c|}{\textbf{Safety}} & \multicolumn{4}{|c}{\textbf{Liveness}} \\
      & atoms & refs & agents & channels & atoms & refs & agents & channels \\
      \hline
      atoms & \n & \n & \n & \n & \y & \y & \y & \n \\
      refs & \n & \y & \y & \n & \y & \y & \y & \n \\
      agents & \y & \y & \y & \y & \y & \y & \y & \n \\
      channels & \y & \y & \y & \y & \y & \y & \n & \n
    \end{tabular}
  \end{frame}

  \begin{frame}
    \frametitle{Possible conflicts}

    \begin{itemize}
      \onslide<1->{
        \item A model reexecutes code containing another model that performs an irrevocable action.
      }
      \vfill
      \onslide<2->{
        \item A model reexecutes code that causes the reexecution to continually happen.
      }
      \vfill
      \onslide<3->{
        \item A model that supports blocking operations is used within a model that does not support blocking operations.
      }
      \vfill
      \onslide<4->{
        \item A model does not guarantee safety or liveness by design, making composability impossible.
      }
    \end{itemize}
  \end{frame}

  \subsection{Future work}

  \begin{frame}
    \frametitle{Future work}

    \begin{itemize}
      \onslide<1->{
        \item Swalens et al.\ planned to identify composable ``building blocks'' (thread creation, message passing, etc.) that could be used to build common concurrency models.~\footcite{Swalens2014}
      }
      \vfill
      \onslide<2->{
        \item Marr and D'Hondt proposed a unifying abstraction for high-level language virtual machines.~\footcite{Marr2012}
      }
      \vfill
      \onslide<3->{
        \item Ziv et al.\ formalized a theory for safely composing concurrency control.~\footcite{Ziv2015}
      }
    \end{itemize}
  \end{frame}

>>>>

\usepackage{appendixnumberbeamer}
\usepackage[USenglish]{babel}
\usepackage[backend=bibtex,citestyle=authortitle]{biblatex}
\usepackage[scale=2]{ccicons}
\usepackage{color}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{multicol}
\usepackage{pifont}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{snakes}

@@

  \begin{frame}
    \frametitle{Threads and processes}

    \begin{figure}
      \centering
      \input{../figures/threads.tikz}
    \end{figure}

    \begin{itemize}
      \item \textbf{Threads} are independent sequences of operations.
      \item \textbf{Processes} are instances of programs made up of one or more threads.
    \end{itemize}
  \end{frame}

@@

  \begin{frame}
    \frametitle{Possible conflicts}
    \centering
    \small

@@

    \vfill
    \begin{tabular}{c | c c c c | c c c c}
      & \multicolumn{4}{c|}{\textbf{Safety}} & \multicolumn{4}{|c}{\textbf{Liveness}} \\
      & atoms & refs & agents & channels & atoms & refs & agents & channels \\
      \hline
      atoms & \n & \n & \n & \n & \y & \y & \y & \n \\
      refs & \n & \y & \y & \n & \y & \y & \y & \n \\
      agents & \y & \y & \y & \y & \y & \y & \y & \n \\
      channels & \y & \y & \y & \y & \y & \y & \n & \n
    \end{tabular}
    \vfill
    \begin{itemize}
      \onslide<2->{
        \item A model reexecutes code that performs an irrevocable action.
      }
      \onslide<3->{
        \item A model reexecutes code that causes the reexecution to continually happen.
      }
      \onslide<4->{
        \item A model that supports blocking operations is used within a model that doesn't.
      }
      \onslide<5->{
        \item A model does not guarantee safety or liveness by design.
      }
    \end{itemize}
  \end{frame}

  \subsection{Ongoing work}

  \begin{frame}
    \frametitle{Ongoing work}

    \begin{itemize}
      \onslide<1->{
        \item Composable ``building blocks'' (thread creation, message passing, etc.) that could be used to build common concurrency models~\footcite{Swalens2014}
      }
      \vfill
      \onslide<2->{
        \item Unifying abstractions for high-level language virtual machines~\footcite{Marr2012}
      }
      \vfill
      \onslide<3->{
        \item Formal theories for safely composing concurrency control~\footcite{Ziv2015}
      }
    \end{itemize}
  \end{frame}
